\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-25 k-planar.tex
I'm happy with this....

\begin{abstract}
Dujmovi\'c~et~al.~[\emph{J.~ACM}~'20] recently proved that every planar graph is isomorphic to a subgraph of the strong product of a graph of bounded treewidth and a path. Analogous results were obtained for graphs of bounded Euler genus or apex-minor-free graphs. These tools have been used to solve longstanding problems on queue layouts, non-repetitive colouring, $p$-centered colouring, and adjacency labelling. This paper proves analogous product structure theorems for various non-minor-closed classes. One noteable example is $k$-planar graphs (those with a drawing in the plane in which each edge is involved in at most $k$ crossings). We prove that every $k$-planar graph is isomorphic to a subgraph of the strong product of a graph of treewidth $O(k^5)$ and a path. This is the first result of this type for a non-minor-closed class of graphs. It implies, amongst other results, that $k$-planar graphs have non-repetitive chromatic number upper-bounded by a function of $k$. All these results generalise for drawings of graphs on arbitrary surfaces. In fact, we work in a much more general setting based on so-called shortcut systems that are of independent interest. This leads to analogous results for certain types of map graphs, string graphs, graph powers, and nearest neighbour graphs.
\end{abstract}
\end{titlepage}
\pagenumbering{roman}
\tableofcontents
\newpage

@@

\begin{compactitem}
\item every path in $\SS$ has length at most $k$,\footnote{A path of length $k$ consists of $k$ edges and $k+1$ vertices.  A path is \defin{trivial} if it has length 0 and \defin{non-trivial} otherwise.} and
\item for every $v\in V(G)$, the number of paths in $\SS$ that use $v$ as an internal vertex is at most $d$.
\end{compactitem}
Each path $P\in\SS$ is called a \defin{shortcut}; if $P$ has endpoints $v$ and $w$ then it is a \defin{$vw$-shortcut}. Given a graph $G$ and a $(k,d)$-shortcut system $\SS$ for $G$, let $G^{\SS}$ denote the supergraph of $G$ obtained by adding the edge $vw$ for each $vw$-shortcut in $\SS$.

@@

The remainder of this paper is organized as follows:
\begin{compactitem}
  \item In \cref{Structure} we prove our main result for shortcut systems (\cref{ShortcutProduct}), and its optimisations for $k$-planar graphs and their genus-$g$ generalisation (\cref{kPlanarProduct,gkPlanarProduct}).
  \item \Cref{examples} uses \cref{ShortcutProduct,kPlanarProduct,gkPlanarProduct} to derive product structure theorems for string graphs, powers of bounded-degree graphs, map graphs, and $k$-nearest neighbour graphs.
  \item \Cref{FramedSection} proves a product structure theorem for $d$-framed multigraphs in which the graph $H$ has treewidth $3$ and is planar.  Using this result, we derive improved product structure theorems for $1$-planar graphs and planar map graphs, again with a planar graph $H$.
  \item \Cref{Applications} quickly surveys applications of product structure and the consequences of the current work.
\end{compactitem}

@@

\begin{proof}
  If $xy\in E(J)$ then there exists a shortcut $P:=v_0,\ldots,v_r\in\SS$ with endpoints $v_0\in S_x$ and $v_r\in S_y$.\footnote{Recall that we have made the assumption that $\SS$ contains a length-$1$ $vw$-shortcut for each edge $vw\in E(G)$.}  For each $i\in\{0,\ldots,r\}$, let $Y_{x_i}$ be the part in $\mathcal{Y}$ that contains $v_i$.  Since $P$ is a connected subgraph of $G$, $H[\{x_0,\ldots,x_r\}]$ is a connected subgraph of $H$.  Since $\mathcal{T}$ is a normalized tree decomposition of $H$, some node $x_i$ is a $T$-ancestor of all nodes in $x_0,\ldots,x_r$.

@@

  Suppose, without loss of generality, that $v_0$ participates in $x_i$.  Then $a(v_0)=x$ is a $T$-ancestor of $x_i$ which a $T$-ancestor of $x_r$.  Finally $a(v_r)=y$ is a $T$-ancestor of $x_r$.  Therefore, both $x$ and $y$ are contained in the path from the root of $T$ to $x_r$, so at least one of $x$ or $y$ is a $T$-ancestor of the other.
\end{proof}

@@

  Therefore $W:=y_0,\ldots,y_s:=x,x_j,x_{j+1},\ldots,x_r$ is a lazy walk in $H^+$ of length $r\le k$.  For each $j\in \{0,\ldots,s\}$, let $z_j$ be the lowest common $T$-ancestor of $y_0,\ldots,y_j$.  The same reasoning used to conclude that $xx_j\in E(H^+)$ can be used to conclude that $z_{i-1}=z_i$ or $z_{i-1}z_i\in E(H^+)$ for each $i\in\{1,\ldots,s\}$.  Therefore $z_0,\ldots,z_s$ is a directed lazy walk in $\overrightarrow{H}^+$.  Finally, let $\overrightarrow{W}$ be the path in $\overrightarrow{H}^+$ obtained by removing removing duplicates from $z_0,\ldots,z_s$.  Then $\overrightarrow{W}$ is a directed path in $\overrightarrow{H}^+$ from $x$ to $a$ of length at most $s\le r\le k$.  This completes the proof.
\end{proof}

@@

\cref{d_framed_product_stucture} is used below to obtain product structure theorems for 1-planar multigraphs and for map graphs.  For simple 1-planar graphs it is essential that we allow frames with parallel edges.

@@

\begin{lem}
	\label{induction} The setup:
	\begin{compactenum}
		\item Let $G$ be a $d$-framed multigraph and let $G_0$ be a frame of $G$.
		\item Let $F_0$ be the outer face of $G_0$ and let $T$ be a BFS spanning forest of $G_0$ rooted at $V(F_0)$.
		\item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
		\item Let $F$ be a cycle in $G'$ that $V(F)$ is partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
		\begin{compactenum}
			\item $F[P_i]$ is connected; and
			\item $P_i$ has a partition $\{X_i,Y_i\}$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
		\end{compactenum}
		\item Let $N$ and $N_0$ be the subgraphs of $G$ and $G_0$ consisting only of those edges and vertices contained in the interior or boundary of $F$.
	\end{compactenum}
	Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
	\begin{compactenum}[(i)]
		\item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
		\item For each $x\in V(H)$, $S_x$ has a partition $\{X_x,Y_x\}$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
		\item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$ then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
	\end{compactenum}
%\note{PM}{I've changed my mind about this notation change.  We end up applying the lemma inductively on the faces $F_1,\ldots,F_m$ of $M$ (which are cycles in $G$).  It makes sense that the original cycle in $G$ is called $F$.}
%\note{DW}{okay}
%\begin{lem}
%  \label{induction} The setup:
%  \begin{compactenum}
%    \item Let $G$ be a $d$-framed multigraph and let $G'$ be a frame of $G$.
%    \item Let $F_0$ be the outer face of $G'$ and let $T$ be a BFS spanning forest of $G'$ rooted at $V(F_0)$.
%    \item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
%    \item Let $F$ be a cycle in $G'$ whose vertices are partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
%    \begin{compactenum}
%      \item $F[P_i]$ is connected; and
%      \item $P_i=Y_i\cup X_i$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
%    \end{compactenum}
%    \item Let $N$ and $N'$ be the subgraphs of $G$ and $G'$ consisting only of those edges and vertices contained in the closure of $F$.
%  \end{compactenum}
%  Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
%  \begin{compactenum}[(i)]
%    \item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
%    \item For each $x\in V(H)$, $S_x=Y_x\cup X_x$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
%    \item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$, then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
%  \end{compactenum}
\end{lem}

@@

	Since $M$ is $2$-connected and $\overline{S}$ is connected, $F_i[P_{i,j}]$ is connected, for each $j\in\{1,2,3\}$.  Let $N_i$ and $N_{0,i}$ be the subgraphs of $N$ and $N_0$ contained in the interior or boundary of $F_i$.  Every inner face of $N_{0,i}$ is an inner face of $N_0$ and $\tau$ is not an inner face of $N_{0,i}$.  Therefore $N_{0,i}$ has fewer inner faces than $N_{0}$.  Therefore, we can apply induction using the cycle $F_i$ and the partition $P_{i,1},P_{i,2},P_{i,3}$ of $V(F_i)$.  The result of the induction is a $H_i$-partition $\mathcal{P}_i$ of $N_i$.
	% The partition $\mathcal{P}_i$ contains each of $P_{i,1}$, $P_{i,2}$ and $P_{i,3}$.
	We can now define our partition
	\[
	\mathcal{P}:=\{Y, P_1,\ldots,P_k\} \cup \bigcup_{i=1}^m \{P\in\mathcal{P}_i: P\cap V(M)=\emptyset\} \enspace .
	\]
	It is straightforward to verify that $\mathcal{P}$ is indeed a partition of $V(N)$ and, by definition this is an $H$-partition of $N$ for the graph $H:=N/\mathcal{P}$.  All that remains is to verify that $\mathcal{P}$ satisfies (i)--(iii).

@@

For each face $F$ of $G_1$ that corresponds to a vertex $x$ of $G_0$, the size of $F$ \note{DW}{Is ``size'' defined? Do we mean length of the facial cycle? } equals the number of nations incident to $x$, which is at most $d$. So every face of $G_1$ has size at most $d$.  Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.  \note{DW}{I like this notation. Should we use it throughout?}

@@

Combining \cref{non-repetitive} with our results on product structure, we obtain the following corollary:
\begin{cor}\label{nonrepetitive_cor}
  The following bounds hold for the nonrepetitive chromatic number of any graph from each of the following classes:
  \begin{compactitem}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+4}{3}}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $1792$
    \item $d$-map: $256(d+3\floor{\frac{d}{2}}-3)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-nearest-neighbour: $4^{O(k^6)}$
    \item $(g,d)$-map graph: $(7d^2-21d)\cdot 4^{10}$
  \end{compactitem}
\end{cor}

Prior to the current work, the strongest upper bound on the non-repetitive chromatic number of $n$-vertex  $k$-planar graphs was $O(k\log n)$ \cite{dujmovic.morin.ea:layered}.  Our results also give bounds on the nonrepetitive chromatic number of $(g,\delta)$-string graphs and $k$-nearest-neighbour graphs, but these bounds are weaker than existing results based on maximum degree.  The bounds obtained from product structure are exponential in $\delta$ and $k^2$, respectively.  However, each of these graph classes has degree bounded by $O(\delta)$ and $O(k^2)$, respectively, and therefore have nonrepetitive chromatic number $O(\delta^2)$ and $O(k^{4})$, respectively \cite{DJKW16}.

@@

As with nonrepetitive chromatic number, our results also imply bounds on the $p$-centered chromatic numer of $(g,\delta)$-string graphs, powers of bounded-degree graphs, and $k$-nearest-neighbour graphs, but these bounds are weaker than the bounds implied by the fact that these graphs have bounded maximum degree \cite{DFMS21}.

>>>>

\begin{abstract}
Dujmovi\'c~et~al.~[\emph{J.~ACM}~'20] recently proved that every planar graph is isomorphic to a subgraph of the strong product of a bounded treewidth graph and a path. Analogous results were obtained for graphs of bounded Euler genus or apex-minor-free graphs. These tools have been used to solve longstanding problems on queue layouts, non-repetitive colouring, $p$-centered colouring, and adjacency labelling. This paper proves analogous product structure theorems for various non-minor-closed classes. One noteable example is $k$-planar graphs (those with a drawing in the plane in which each edge is involved in at most $k$ crossings). We prove that every $k$-planar graph is isomorphic to a subgraph of the strong product of a graph of treewidth $O(k^5)$ and a path. This is the first result of this type for a non-minor-closed class of graphs. It implies, amongst other results, that $k$-planar graphs have non-repetitive chromatic number upper-bounded by a function of $k$. All these results generalise for drawings of graphs on arbitrary surfaces. In fact, we work in a much more general setting based on so-called shortcut systems that are of independent interest. This leads to analogous results for certain types of map graphs, string graphs, graph powers, and nearest neighbour graphs.
\end{abstract}
\end{titlepage}
\pagenumbering{roman}
\tableofcontents
\newpage

@@

\begin{compactitem}
\item every path in $\SS$ has length at most $k$,\footnote{A path of length $k$ consists of $k$ edges and $k+1$ vertices.  A path is \defin{trivial} if it has length 0 and \defin{non-trivial} otherwise.} and
\item for every $v\in V(G)$, the number of paths in $\SS$ that include $v$ as an internal vertex is at most $d$.
\end{compactitem}
Each path $P\in\SS$ is called a \defin{shortcut}; if $P$ has endpoints $v$ and $w$ then it is a \defin{$vw$-shortcut}. Given a graph $G$ and a $(k,d)$-shortcut system $\SS$ for $G$, let $G^{\SS}$ denote the supergraph of $G$ obtained by adding the edge $vw$ for each $vw$-shortcut in $\SS$.

@@

The remainder of this paper is organized as follows:
\begin{compactitem}
  \item In \cref{Structure} we prove our main result for shortcut systems (\cref{ShortcutProduct}), and its optimisations for $k$-planar graphs and their genus-$g$ generalisation (\cref{kPlanarProduct,gkPlanarProduct}).
  \item \Cref{examples} uses \cref{ShortcutProduct,kPlanarProduct,gkPlanarProduct} to derive product structure theorems for string graphs, powers of bounded-degree graphs, map graphs, and $k$-nearest neighbour graphs.
  \item \Cref{FramedSection} proves a product structure theorem for $d$-framed multigraphs in which the graph $H$ has treewidth $3$ and is planar.  Using this result, we derive improved product structure theorems for $1$-planar graphs and planar map graphs, again with a planar graph $H$.
  \item \Cref{Applications} quickly surveys applications of product structure theorems and the consequences of the current work.
\end{compactitem}

@@

\begin{proof}
  If $xy\in E(J)$ then there exists a shortcut $P:=v_0,\ldots,v_r\in\SS$ with endpoints $v_0\in S_x$ and $v_r\in S_y$.\footnote{Recall that we have made the assumption that $\SS$ contains a length-$1$ $vw$-shortcut for each edge $vw\in E(G)$.}  For each $i\in\{0,\ldots,r\}$, let $Y_{x_i}$ be the part in $\mathcal{Y}$ that contains $v_i$.  Since $P$ is a connected subgraph of $G$, $H[\{x_0,\ldots,x_r\}]$ is a connected subgraph of $H$.  Since $\mathcal{T}$ is a normalized tree decomposition of $H$, \tref{ancestor-edge} implies that some node $x_i$ is a $T$-ancestor of all nodes in $x_0,\ldots,x_r$.

@@

  Suppose, without loss of generality, that $v_0$ participates in $x_i$.  Then $a(v_0)=x$ is a $T$-ancestor of $x_i$ which a $T$-ancestor of $x_r$.  Finally $a(v_r)=y$ is a $T$-ancestor of $x_r$.  Therefore, both $x$ and $y$ are contained in the path from the root of $T$ to $x_r$, so at least one of $x$ or $y$ is a $T$-ancestor of the other.  This completes the proof of \cref{i-ancestor}
\end{proof}

@@

  Therefore $W:=y_0,\ldots,y_s:=x,x_j,x_{j+1},\ldots,x_r$ is a lazy walk in $H^+$ of length $r\le k$.  For each $j\in \{0,\ldots,s\}$, let $z_j$ be the lowest common $T$-ancestor of $y_0,\ldots,y_j$.  The same reasoning used to conclude that $xx_j\in E(H^+)$ can be used to conclude that $z_{i-1}=z_i$ or $z_{i-1}z_i\in E(H^+)$ for each $i\in\{1,\ldots,s\}$.  Therefore $z_0,\ldots,z_s$ is a directed lazy walk in $\overrightarrow{H}^+$.  Finally, let $\overrightarrow{W}$ be the path in $\overrightarrow{H}^+$ obtained by removing removing duplicates from $z_0,\ldots,z_s$.  Then $\overrightarrow{W}$ is a directed path in $\overrightarrow{H}^+$ from $x$ to $a$ of length at most $s\le r\le k$.  This completes the proof of \cref{general-bag-size}.
\end{proof}

@@

\cref{d_framed_product_stucture} is used below to obtain product structure theorems for 1-planar multigraphs and for map graphs.  Even for simple 1-planar graphs it is essential that we allow frames with parallel edges.

@@

\begin{lem}
	\label{induction} The setup:
	\begin{compactenum}
		\item Let $G$ be a $d$-framed multigraph and let $G_0$ be a frame of $G$.
		\item Let $F_0$ be the outer face of $G_0$ and let $T$ be a BFS spanning forest of $G_0$ rooted at $V(F_0)$.
		\item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
		\item Let $F$ be a cycle in $G_0$ whose vertices are partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
		\begin{compactenum}
			\item $F[P_i]$ is connected; and
			\item $P_i$ has a partition $\{X_i,Y_i\}$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
		\end{compactenum}
		\item Let $N$ and $N_0$ be the subgraphs of $G$ and $G_0$ consisting only of those edges and vertices contained in the interior or boundary of $F$.
	\end{compactenum}
	Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
	\begin{compactenum}[(i)]
		\item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
		\item For each $x\in V(H)$, $S_x$ has a partition $\{X_x,Y_x\}$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
		\item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$ then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
	\end{compactenum}
%\note{PM}{I've changed my mind about this notation change.  We end up applying the lemma inductively on the faces $F_1,\ldots,F_m$ of $M$ (which are cycles in $G$).  It makes sense that the original cycle in $G$ is called $F$.}
%\note{DW}{okay}
%\begin{lem}
%  \label{induction} The setup:
%  \begin{compactenum}
%    \item Let $G$ be a $d$-framed multigraph and let $G'$ be a frame of $G$.
%    \item Let $F_0$ be the outer face of $G'$ and let $T$ be a BFS spanning forest of $G'$ rooted at $V(F_0)$.
%    \item For every integer $j\ge 0$, let $L_j=\{v\in V(G):\dist_T(v,V(F_0))=j\}$.
%    \item Let $F$ be a cycle in $G'$ whose vertices are partitioned into $k\le 3$ sets $P_1,\ldots,P_k$ such that for each $i\in\{1,\ldots,k\}$,
%    \begin{compactenum}
%      \item $F[P_i]$ is connected; and
%      \item $P_i=Y_i\cup X_i$ where $|X_i|\le d-3$ and $|Y_i\cap L_j| \le 3$ for each $j\ge 0$.
%    \end{compactenum}
%    \item Let $N$ and $N'$ be the subgraphs of $G$ and $G'$ consisting only of those edges and vertices contained in the closure of $F$.
%  \end{compactenum}
%  Then $N$ has an $H$-partition $\PP=\{S_x: x\in V(H)\}$ such that:
%  \begin{compactenum}[(i)]
%    \item for each $i\in\{1,\ldots,k\}$, there exists $x_i\in V(H)$ such that $P_i=S_{x_i}$;
%    \item For each $x\in V(H)$, $S_x=Y_x\cup X_x$ where $|X_x|\le d-3$ and $|Y_x\cap L_j|\le 3$ for each $j\ge 0$;
%    \item $H$ has a $3$-simple tree decomposition $\mathcal{T}$ and, if $k=3$, then $\{x_1,x_2,x_3\}$ is contained in exactly one bag of $\mathcal{T}$.
%  \end{compactenum}
\end{lem}

@@

	Since $M$ is $2$-connected and $\overline{S}$ is connected, $F_i[P_{i,j}]$ is connected, for each $j\in\{1,2,3\}$.  Let $N_i$ and $N_{0,i}$ be the subgraphs of $N$ and $N_0$ contained in the interior or boundary of $F_i$.  Every inner vertex of $N_{0,i}$ is an inner vertex of $N_{0}$.  Every inner face of $N_{0,i}$ is an inner face of $N_0$ and $\tau$ is not an inner face of $N_{0,i}$.  Therefore $N_{0,i}$ has no more inner vertices than $N_0$ and has fewer inner faces than $N_{0}$.  Therefore, we can apply induction using the cycle $F_i$ and the partition $P_{i,1},P_{i,2},P_{i,3}$ of $V(F_i)$.  The result of the induction is a $H_i$-partition $\mathcal{P}_i$ of $N_i$.
	% The partition $\mathcal{P}_i$ contains each of $P_{i,1}$, $P_{i,2}$ and $P_{i,3}$.
	We can now define our partition
	\[
	\mathcal{P}:=\{Y, P_1,\ldots,P_k\} \cup \bigcup_{i=1}^m \{P\in\mathcal{P}_i: P\cap V(M)=\emptyset\} \enspace .
	\]
	It is straightforward to verify that $\mathcal{P}$ is indeed a partition of $V(N)$ and, by definition this is an $H$-partition of $N$ for the graph $H:=N/\mathcal{P}$.  All that remains is to verify that $\mathcal{P}$ satisfies (i)--(iii).

@@

For each face $F$ of $G_1$ that corresponds to a vertex $x$ of $G_0$, the size of $F$ \note{DW}{Is ``size'' defined? Do we mean length of the facial cycle? } equals the number of nations incident to $x$, which is at most $d$. So every face of $G_1$ has size at most $d$.  Let $\widehat{G}_1$ be the $d$-framed graph whose frame is $G_1$.  \note{DW}{I like this notation. Should we use it throughout?} \note{PM}{No. For most things I prefer $G$ and $G_0$ rather than $\widehat{G}_0$ and $G_0$.}

@@

Combining \cref{non-repetitive} with our results on product structure, we obtain the following corollary:
\begin{cor}\label{non-repetitive_cor}
  The following bounds hold for the non-repetitive chromatic number of any graph from each of the following classes:
  \begin{compactitem}
    \item $k$-planar: $(18k^2+48k+30)\cdot 4^{\binom{k+4}{3}}$
    \item $(g,k)$-planar: $\max\{2g,3\}\cdot(6k^2+16k+10) 4^{\binom{k+4}{3}}$
    % \item $(g,\delta)$-string: $g4^{O(\delta^3)}$
    \item $1$-planar: $1792$
    \item $d$-map: $256(d+3\floor{\frac{d}{2}}-3)$
    % \item $(g,d)$-map: $g4^{O(d)}$
    % \item $k$-nearest-neighbour: $4^{O(k^6)}$
    \item $(g,d)$-map graph: $(7d^2-21d)\cdot 4^{10}$
  \end{compactitem}
\end{cor}

Prior to the current work, the strongest upper bound on the non-repetitive chromatic number of $n$-vertex  $k$-planar graphs was $O(k\log n)$ \cite{dujmovic.morin.ea:layered}.  Our results also give bounds on the non-repetitive chromatic number of $(g,\delta)$-string graphs and $k$-nearest-neighbour graphs, but these bounds are weaker than existing results based on maximum degree.  The bounds obtained from product structure are exponential in $\delta$ and $k^2$, respectively.  However, each of these graph classes has degree bounded by $O(\delta)$ and $O(k^2)$, respectively, and therefore have non-repetitive chromatic number $O(\delta^2)$ and $O(k^{4})$, respectively \cite{DJKW16}.

@@

As with non-repetitive chromatic number, our results also imply bounds on the $p$-centered chromatic numer of $(g,\delta)$-string graphs, powers of bounded-degree graphs, and $k$-nearest-neighbour graphs, but these bounds are weaker than the bounds implied by the fact that these graphs have bounded maximum degree \cite{DFMS21}.
